%!TEX encoding = UTF8
%!TEX root =Demircan_cv.tex

\begin{rubric}{Peer-Reviewed Publications \& Preprints}
    \entry*[2026]
    \textbf{Demircan, C.}, Binz, M., Modirshanechi, A., \& Schulz, E. Meta-learning as a principle for human-like visual representations. \emph{Under Review.} {\href{https://arxiv.org/abs/2606.28399}{\textcolor{MarkerColour}{\lbrack\texttt{paper}\rbrack}}} {\href{https://github.com/candemircan/metalign}{\textcolor{MarkerColour}{\lbrack\texttt{code \& data}\rbrack}}} \par

    \entry*[2026]
    Binz, M., \ldots  , \textbf{Demircan, C.}, \ldots  , Schulz, E. Post-training makes large language models less human-like. \emph{Under Review.} {\href{https://arxiv.org/abs/2605.07632}{\textcolor{MarkerColour}{\lbrack\texttt{paper}\rbrack}}} \par

    \entry*[2026]
    Schulze Buschoff, L. M., Voudouris, K., \textbf{Demircan, C.}, \& Schulz, E. Can Vision Language Models Learn Intuitive Physics from Interaction? \emph{International Conference on Machine Learning (ICML).} {\href{https://arxiv.org/abs/2602.06033}{\textcolor{MarkerColour}{\lbrack\texttt{paper}\rbrack}}} \par

    \entry*[2025]
    Saanum, T.*, \textbf{Demircan, C.}*, Gershman, S. J., \& Schulz, E. A circuit for predicting hierarchical structure in-context in Large Language Models. \emph{Under Review.} {\href{https://www.arxiv.org/abs/2509.21534}{\textcolor{MarkerColour}{\lbrack\texttt{paper}\rbrack}}} {\href{https://github.com/tankred-saanum/smart_induction_heads}{\textcolor{MarkerColour}{\lbrack\texttt{code}\rbrack}}} \par

	\entry*[2025]
	Binz, M., \ldots  , \textbf{Demircan, C.}, \ldots  , Schulz, E. A foundation model to predict and capture human cognition. \emph{Nature}. {\href{https://www.nature.com/articles/s41586-025-09215-4}{\textcolor{MarkerColour}{\lbrack\texttt{paper}\rbrack}}} \par

    \entry*[2025]
    \textbf{Demircan, C.}*, Saanum, T.*, Jagadish, A. K., Binz, M., \& Schulz, E. Sparse Autoencoders Reveal Temporal Difference Learning in Large Language Models. \emph{International Conference on Learning Representations (ICLR).} {\href{https://openreview.net/forum?id=2tIyA5cri8}{\textcolor{MarkerColour}{\lbrack\texttt{paper}\rbrack}}} \par

    \entry*[2024]
    \textbf{Demircan, C.}, Saanum, T., Pettini, L., Binz, M., Baczkowski, B. M., Doeller, C., Garvert, M. M., \& Schulz, E. Evaluating alignment between humans and neural network representations in image-based learning tasks. \emph{Advances in Neural Information Processing Systems (NeurIPS).} {\href{https://openreview.net/forum?id=8i6px5W1Rf&referrer=%5Bthe%20profile%20of%20Eric%20Schulz%5D(%2Fprofile%3Fid%3D~Eric_Schulz1)}{\textcolor{MarkerColour}{\lbrack\texttt{paper}\rbrack}}} {\href{https://github.com/candemircan/naturalcogsci}{\textcolor{MarkerColour}{\lbrack\texttt{code}\rbrack}}} {\href{https://osf.io/h3t52/}{\textcolor{MarkerColour}{\lbrack\texttt{data}\rbrack}}} \par

    \entry*[2024]
    Özdemir, Ş., Şentürk, Y. D., Ünver, N., \textbf{Demircan, C.}, Olivers, C. N. L., Egner, T., \& Günseli, E. Effects of context changes on memory reactivation. \emph{Journal of Neuroscience}. {\href{https://www.jneurosci.org/content/44/36/e2096232024.abstract}{\textcolor{MarkerColour}{\lbrack\texttt{paper}\rbrack}}} \par

    \entry*[2024]
    Şentürk, Y. D., Ünver, N., \textbf{Demircan, C.}, Egner, T., \& Günseli, E. The reactivation of task rules triggers the reactivation of task-relevant items. \emph{Cortex}. {\href{https://www.sciencedirect.com/science/article/abs/pii/S0010945223002903}{\textcolor{MarkerColour}{\lbrack\texttt{paper}\rbrack}}} \par


\end{rubric}